---
title: "00_Soil_Order_Classification"
author: "pdsewll"
date: "2023-03-15"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(reshape)
require(reshape2)
require(vegan)
require(caret)
require(tcltk)
require(randomForest)
require(Matrix)
require(labdsv)
require(gdata)
require(MASS)
require(openxlsx)
require (C50)
require(tidyr)
require(stringr)
require(rpart)
require(tree)
require(rattle)
require(rpart.plot)
require(partykit)
require(vegclust)
require(standardize)
require(dplyr)
require(tictoc)
require(plyr)
require(Hmisc)
require(data.table)
require(tidyverse)
require(psych)
require(DataExplorer)

<<<<<<< HEAD
```
# Background

This script links to a VPRO database and brings in _MIN, _HMS, for classification 
1. Creates classification using a list to store results, faster than previous R bind solution
2. Improve filters for pretreatment, and refined classification
3. Soil texture fixes


---{r import data}

#PDS: can't open access database without key. I instead opened the BECMaster64_Mineral as an xlsx workbook, and _Humus. See next chunk.

```{r Import excel workbooks, echo = TRUE}
setwd("C:/Users/pauld/Documents/23_BEC_Cleaning/BECMaster_Cleaning")
plot.hum <- readxl::read_xlsx("../access_data/BECMaster64_Humus.xlsx")
plot.min <- readxl::read_xlsx("../access_data/BECMaster64_Mineral.xlsx")
```

```{r Modify Humus and Mineral dataframes, echo = TRUE}


##Humus
plot.hum2 <- plot.hum %>% dplyr::select(PlotNumber, Horizon, UpperDepth, LowerDepth, Comment) %>% dplyr::rename(Comments = Comment, UpperDepth = LowerDepth, LowerDepth = UpperDepth) %>% mutate(Depth = UpperDepth - LowerDepth) #reorder upper and lower depths since LFH/O Horizons

plot.hum2 <- plot.hum2 %>% mutate(newUpperDepth = ifelse(Depth<0, LowerDepth, UpperDepth)) %>% 
    mutate(newLowerDepth = ifelse(Depth<0, UpperDepth,LowerDepth)) %>%
    mutate(newDepth = newUpperDepth - newLowerDepth) %>% dplyr::select(-UpperDepth, -LowerDepth, -Depth) %>% 
  mutate(Texture = "Org", origin = "Humus")

plot.hum2$Horizon <- stringr::str_replace_all(plot.hum2$Horizon, "-", "")
plot.hum2$Horizon <- stringr::str_replace_all(plot.hum2$Horizon, " ", "")
plot.hum2$Horizon <- stringr::str_replace_all(plot.hum2$Horizon, "\\(", "")
plot.hum2$Horizon <- stringr::str_replace_all(plot.hum2$Horizon, "\\)", "")
plot.hum2$Horizon <- stringr::str_replace_all(plot.hum2$Horizon, "/", "")

unique(plot.hum2$Horizon)

#Filter entries horizons that are NOT organic (ie A,B,C), then calculate cumulative organic thickness. Also Excluding buried horizons; drawback of filtering buried horizons- may exclude some organics from being classified ie Om, Hb, Oh, A,B,C
plot.hum3 <- plot.hum2 %>% filter(!Horizon %in% c(grep("^A(?!sh)|^B|^C(?!har)|
                                                       ^IA(?!sh)|^IB|^IC(?!har)|
                                                       ^IIA(?!sh)|^IIB|^IIC(?!har)|
                                                       ^IIIA(?!sh)|^IIIB|^IIIC(?!har)|
                                                       ^IVA(?!sh)|^IVB|^IVC(?!har)|
                                                       ^VA(?!sh)|^VB|^VC(?!har)|
                                                       ^VIA(?!sh)|^VIB|^VIC(?!har)|
                                                       ^VIIA(?!sh)|^VIIB|^VIIC(?!har)|
                                                       ^VIIIA(?!sh)|^VIIIB|^VIIIC(?!har)|
                                                       ^1A(?!sh)|^1B|^1C(?!har)|
                                                       ^2A(?!sh)|^2B|^2C(?!har)|
                                                       ^3A(?!sh)|^3B|^3C(?!har)|
                                                       ^4A(?!sh)|^4B|^4C(?!har)|
                                                       ^5A(?!sh)|^5B|^5C(?!har)|
                                                       ^6A(?!sh)|^6B|^6C(?!har)|
                                                       ^7A(?!sh)|^7B|^7C(?!har)|
                                                       ^8A(?!sh)|^8B|^8C(?!har)|^R", plot.hum2$Horizon, perl = TRUE, value = TRUE, ignore.case = TRUE), 
                                                  grep("b", plot.hum2$Horizon, perl = TRUE, value = TRUE, ignore.case = FALSE)))  %>%  
group_by(PlotNumber) %>% dplyr::mutate(Cuml.Thickness = sum(newDepth, na.rm = TRUE)) #Cumulative thickness for classification

plot.hum4 <- plot.hum2 %>% filter(Horizon %in% c(grep("^A(?!sh)|^B|^C(?!har)|
                                                       ^IA(?!sh)|^IB|^IC(?!har)|
                                                       ^IIA(?!sh)|^IIB|^IIC(?!har)|
                                                       ^IIIA(?!sh)|^IIIB|^IIIC(?!har)|
                                                       ^IVA(?!sh)|^IVB|^IVC(?!har)|
                                                       ^VA(?!sh)|^VB|^VC(?!har)|
                                                       ^VIA(?!sh)|^VIB|^VIC(?!har)|
                                                       ^VIIA(?!sh)|^VIIB|^VIIC(?!har)|
                                                       ^VIIIA(?!sh)|^VIIIB|^VIIIC(?!har)|
                                                       ^1A(?!sh)|^1B|^1C(?!har)|
                                                       ^2A(?!sh)|^2B|^2C(?!har)|
                                                       ^3A(?!sh)|^3B|^3C(?!har)|
                                                       ^4A(?!sh)|^4B|^4C(?!har)|
                                                       ^5A(?!sh)|^5B|^5C(?!har)|
                                                       ^6A(?!sh)|^6B|^6C(?!har)|
                                                       ^7A(?!sh)|^7B|^7C(?!har)|
                                                       ^8A(?!sh)|^8B|^8C(?!har)|^R", plot.hum2$Horizon, perl = TRUE, value = TRUE, ignore.case = TRUE), 
                                                  grep("b", plot.hum2$Horizon, perl = TRUE, value = TRUE, ignore.case = FALSE)))                 
                                                            
plot.hum5 <- rbind(plot.hum3, plot.hum4)

plot.hum5$Flag <- "NULL" #For rbind with Mineral

plot.hum5$MineralFormpH <- "NULL"

##Mineral
plot.min2 <- plot.min %>% dplyr::select(PlotNumber, Horizon, UpperDepth, LowerDepth, Texture, Comments, MineralFormpH) %>% 
  mutate(Depth = LowerDepth - UpperDepth)

plot.min2 <- plot.min2 %>% mutate(newUpperDepth = ifelse(Depth<0, LowerDepth, UpperDepth)) %>% 
    mutate(newLowerDepth = ifelse(Depth<0, UpperDepth,LowerDepth)) %>%
    mutate(newDepth = newLowerDepth - newUpperDepth) %>% dplyr::select(-UpperDepth, -LowerDepth, -Depth) %>% 
  mutate(Cuml.Thickness = 0, origin = "Mineral") #Cuml.Thickness created for rbind operation

#new changes to mineral
#Remove Whitespace and some special characters in Horizons

plot.min2$Horizon <- stringr::str_replace_all(plot.min2$Horizon, " ", "")
plot.min2$Horizon <- stringr::str_replace_all(plot.min2$Horizon, "\\(", "")
plot.min2$Horizon <- stringr::str_replace_all(plot.min2$Horizon, "\\)", "")
plot.min2$Horizon <- stringr::str_replace_all(plot.min2$Horizon, "/", "")
plot.min2$Horizon <- stringr::str_replace_all(plot.min2$Horizon, "-", "")

#Filter Special  Characters and '0'
filter_characters <- plot.min2 %>% filter(Horizon %in% c(grep("0", plot.min2$Horizon, perl = TRUE, value = TRUE, ignore.case = FALSE),
                                                             #Keep  '?' for now-#      grep("\\?", plot.min2$Horizon, perl = TRUE, value = TRUE, ignore.case = FALSE),
                                                             grep("\\@", plot.min2$Horizon, perl = TRUE, value = TRUE, ignore.case = FALSE),
                                                             grep("\\*", plot.min2$Horizon, perl = TRUE, value = TRUE, ignore.case = FALSE),
                                                             grep("\\[]", plot.min2$Horizon, perl = TRUE, value = TRUE, ignore.case = FALSE),
                                                             grep("\\!",plot.min2$Horizon, perl = TRUE, value = TRUE, ignore.case = FALSE)))
 
PlotNumber_list <- as.list(unique(filter_characters$PlotNumber))


plot.min.filter2 <- plot.min2 %>% dplyr::filter(!PlotNumber %in% PlotNumber_list)

#Flag PlotNumbers that do not have some combination of A,B,C,R, (I-VIII / 1-8) where Upper Depth is != 0. additionally Excluding "ASH" and "CHAR" 
flag_plots <- plot.min2 %>% filter(Horizon %in% c(grep("^A(?!sh)|^B|^C(?!har)|
                                                       ^IA(?!sh)|^IB|^IC(?!har)|
                                                       ^IIA(?!sh)|^IIB|^IIC(?!har)|
                                                       ^IIIA(?!sh)|^IIIB|^IIIC(?!har)|
                                                       ^IVA(?!sh)|^IVB|^IVC(?!har)|
                                                       ^VA(?!sh)|^VB|^VC(?!har)|
                                                       ^VIA(?!sh)|^VIB|^VIC(?!har)|
                                                       ^VIIA(?!sh)|^VIIB|^VIIC(?!har)|
                                                       ^VIIIA(?!sh)|^VIIIB|^VIIIC(?!har)|
                                                       ^1A(?!sh)|^1B|^1C(?!har)|
                                                       ^2A(?!sh)|^2B|^2C(?!har)|
                                                       ^3A(?!sh)|^3B|^3C(?!har)|
                                                       ^4A(?!sh)|^4B|^4C(?!har)|
                                                       ^5A(?!sh)|^5B|^5C(?!har)|
                                                       ^6A(?!sh)|^6B|^6C(?!har)|
                                                       ^7A(?!sh)|^7B|^7C(?!har)|
                                                       ^8A(?!sh)|^8B|^8C(?!har)|^R",
                                                       plot.min2$Horizon, perl = TRUE, value = TRUE, ignore.case = TRUE)) & newUpperDepth ==0)


flag_list <- as.list(unique(flag_plots$PlotNumber))
plot.min2 <- mutate(plot.min2, Flag = ifelse(!plot.min2$PlotNumber %in% flag_list, "Mineral_Flag", "NULL")) #10,586 entries have been flagged. Many of these include profiles with NAs for depths/horizons, or single horizon plots

plot.soil <- rbind(plot.min2, plot.hum5)

```

```{r organic fix?}

org.corr <- dplyr::filter(plot.soil, Horizon %in% c(grep("^Om(?!b)", plot.soil$Horizon, perl = TRUE, value = TRUE, ignore.case =TRUE))) %>%  group_by(PlotNumber) %>% dplyr::mutate(Cuml.Thickness2 = sum(newDepth, na.rm = TRUE)) #Make a cumulative Om horizon
unique(org.corr$Horizon)

org.corr2 <- plot.soil %>% filter(Horizon %in% grep("^Om|^Of|^Oh|^L(?!ithic)(?!ayer)|^F(?!rozen)(?!rag)|^H(?!ardpan)", plot.soil$Horizon, perl = TRUE, value = TRUE, ignore.case =TRUE) & !Horizon %in% grep("b", plot.soil$Horizon, perl = TRUE, value = TRUE, ignore.case =TRUE)) %>%  group_by(PlotNumber) %>% dplyr::mutate(Cuml.Thickness3 = sum(newDepth, na.rm = TRUE)) %>% select(PlotNumber, Horizon, Cuml.Thickness3)

org.corr3 <- dplyr::full_join(soil_order, org.corr2)
unique(org.corr2$Horizon)


```

```{r Parallel loops for order}
library(foreach)
library(doParallel)
plot.soil2 <- plot.soil
plot.soil2 <- plot.soil2 %>% dplyr::filter(Flag != "Mineral_Flag")


cores=detectCores()
cl = makeCluster(cores[1]-1) 
registerDoParallel(cl)
plots <- unique(plot.soil2$PlotNumber)
plots

system.time(
  
 x <- foreach(i = plots) %dopar% {
  
    plot_sub <- plot.soil2[plot.soil2$PlotNumber==i,]

    cryosol_test <-  dplyr::filter(plot_sub, Horizon %in% grep("(?<!H)(?<!F)(?<!y)(?<!Fa)(?<!Fm)(?<!Hh)(?<!Ha)(?<!L)(?<!Hm)(?<!H1)(?<!H2)(?<!Hd)(?<!Fq)z(?!j)|
(?<!H)(?<!F)(?<!y)(?<!Fa)(?<!Fm)(?<!Hh)(?<!Ha)(?<!L)(?<!Hm)(?<!H1)(?<!H2)(?<!Hd)(?<!Fq)Z(?!j)",  plot_sub$Horizon, perl = TRUE, value = TRUE, ignore.case = FALSE) & newUpperDepth <=100)
    
     
    organic_test_1 <-  dplyr::filter(plot_sub, Horizon %in% grep("Of", plot_sub$Horizon, perl = TRUE, value = TRUE, ignore.case = TRUE) & newDepth >= 60)
    organic_test_2 <-  dplyr::filter(plot_sub, Horizon %in% grep("Om|Oh|LFH|O(?!f)(?!ck)(?!ne)", plot_sub$Horizon, perl = TRUE, value = TRUE, ignore.case = TRUE) & newDepth >= 40)
    organic_test_3 <-  dplyr::filter(plot_sub, Cuml.Thickness >= 60)

     
    vertisol_test_1 <-  dplyr::filter(plot_sub, Horizon %in% grep("(?<!l)v(?!j)", plot_sub$Horizon, perl = TRUE, value = TRUE, ignore.case = TRUE) & newUpperDepth <= 100) #FLAG
    vertisol_test_2 <-  dplyr::filter(plot_sub, Horizon %in% grep("(?<!o)ss(?!j)", plot_sub$Horizon, perl = TRUE, value = TRUE, ignore.case = TRUE) & newUpperDepth <= 100 & Texture != "Org") #Texture is used sparingly- in case mineral entries were included in the Humus file
 
      
    podzol_test1 <- dplyr::filter(plot_sub, Horizon %in% grep("Bf(?!j)|Bhf(?!j)|Bh(?!j)",  plot_sub$Horizon, perl =TRUE, value = T, ignore.case = T) & newDepth >=10)
   
   podzol_test2 <- dplyr::filter(plot_sub, Horizon %in% grep("bt(?!j)",  plot_sub$Horizon, perl =TRUE, value = T, ignore.case = T) & newUpperDepth <=50) #FLAG
    
    gleysol_test1 <- dplyr::filter(plot_sub, Horizon %in% grep("g(?!j)", plot_sub$Horizon, perl = TRUE, value = TRUE, ignore.case = TRUE) &  newUpperDepth <=50)
    
  
    solonetzic_test <-  dplyr::filter(plot_sub, Horizon %in% grep("Bn(?!j)",  plot_sub$Horizon, perl = TRUE, value = TRUE, ignore.case = TRUE))
     
    
    chernozem_test <-  dplyr::filter(plot_sub, Horizon %in% grep("Ah(?!j)(?!b)|Ahe(?!j)(?!b)|Ap(?!j)(?!b)",  plot_sub$Horizon, perl = TRUE, value = TRUE, ignore.case = TRUE) & newDepth >= 10)
    
    
   luvisol_test <-  dplyr::filter(plot_sub, Horizon %in% grep("Bt(?!j)",  plot_sub$Horizon, perl = TRUE, value = TRUE, ignore.case = TRUE) & newDepth >= 5)
   
    brunisol_test <-  dplyr::filter(plot_sub, Horizon %in% grep("B",  plot_sub$Horizon, perl = TRUE, value = TRUE, ignore.case = FALSE), !Horizon %in% grep("b",  plot_sub$Horizon, perl = TRUE, value = TRUE, ignore.case = FALSE) & newDepth >= 5) #this might be a problem with buried horizons, have taken out the ignore case element for now
    
  ##### FIX SYNTAX  BRUNISOL_TEST <- dplyr::filter(plot.soil, Horizon %in% c(grep("B"|"!b"  plot.soil$Horizon, perl = TRUE, value = TRUE, ignore.case = FALSE) & newDepth >= 5  &  grep("b",  plot.soil$Horizon, perl = TRUE, value = TRUE, ignore.case = FALSE))
    
    #Try filtering B horizons, that don't also include a lowercase b
    
    
    ##Indeed a problem for buried horizons: ie IC, Bmb, IIC <- Classified as Brunisol, but Should be Regosol. 
   
    regosol_test <- dplyr::filter(plot_sub, newDepth >= 0)
    
 order <-  dplyr::if_else(nrow(cryosol_test) >= 1,  "Cryosol", 
    dplyr::if_else(nrow(organic_test_1) >= 1 | nrow(organic_test_2) >= 1 | nrow(organic_test_3) >= 1, "Organic", 
      dplyr::if_else(nrow(vertisol_test_1) >=1 & nrow(vertisol_test_2) >=1, "Vertisol", 
        dplyr::if_else(nrow(podzol_test1)>=1 & nrow(podzol_test2) <1, "Podzol",
          dplyr::if_else(nrow(gleysol_test1)>=1, "Gleysol", 
            dplyr::if_else(nrow(solonetzic_test) >= 1, "Solonetzic", 
              dplyr::if_else(nrow(chernozem_test) >= 1, "Chernozem", 
                dplyr::if_else(nrow(luvisol_test) >= 1, "Luvisol", 
                  dplyr::if_else(nrow(brunisol_test_1) >= 1 & nrow(brunisol_test_2) < 1, "Brunisol",
                    dplyr::if_else(nrow(regosol_test) >=1, "Regosol", 
                           "FALSE"))))))))))

  return(list(i, order))
 }
)
dat2 <- rbindlist(x) %>% dplyr::rename(PlotNumber = V1, Order = V2)
X1 <- full_join(dat2, plot.soil2)
```



```{r Loops for soil orders}

plot.soil2 <- plot.soil %>% dplyr::filter(Flag != "Mineral_Flag")
plot.soil2 <- plot.soil2[1:1000,]
order_list <- list()
plots <- unique(plot.soil2$PlotNumber)

system.time(
  for (i in plots){
  try({
    
    plot_sub <- plot.soil2[plot.soil2$PlotNumber==i,]

        #OPTION 1: Gone through list of entries, more complicated string for grep  
        cryosol_test <- filter(plot_sub, Horizon %in% grep("(?<!H)(?<!F)(?<!y)(?<!Fa)(?<!Fm)(?<!Hh)(?<!Ha)(?<!L)(?<!Hm)(?<!H1)(?<!H2)(?<!Hd)(?<!Fq)z(?!j)|
(?<!H)(?<!F)(?<!y)(?<!Fa)(?<!Fm)(?<!Hh)(?<!Ha)(?<!L)(?<!Hm)(?<!H1)(?<!H2)(?<!Hd)(?<!Fq)Z(?!j)",  plot_sub$Horizon, perl = TRUE, value = TRUE, ignore.case = FALSE) & newUpperDepth <=100)
    
    #OPTION 2: Simple, only uses Z entries from mineral- could miss Oz entries in humus form sheet
  #      cryosol_test <- filter(plot_sub, Horizon %in% grep("z(?!j)",  plot_sub$Horizon, perl = TRUE, value = TRUE, ignore.case = FALSE) & newUpperDepth <=100 & origin = "Mineral")

    cryosol <- ifelse(nrow(cryosol_test) >= 1,  "Cryosol", "FALSE")
      
    order_list[[i]] <- cryosol
      
      if(order_list[[i]] =="Cryosol")
      {next}
     
    
    organic_test_1 <- filter(plot_sub, Horizon %in% grep("Of", plot_sub$Horizon, perl = TRUE, value = TRUE, ignore.case = TRUE) & newDepth >= 60)
    organic_test_2 <- filter(plot_sub, Horizon %in% grep("Om|Oh|LFH|O(?!f)(?!ck)(?!ne)", plot_sub$Horizon, perl = TRUE, value = TRUE, ignore.case = TRUE) & newDepth >= 40)
    organic_test_3 <- filter(plot_sub, Cuml.Thickness >= 60)

    organic <- ifelse(nrow(organic_test_1) >= 1 | nrow(organic_test_2) >= 1 | nrow(organic_test_3) >= 1, "Organic", "FALSE")    
      
    order_list[[i]] <- organic
      
    
      if(order_list[[i]] =="Organic")
      {next}
    
   
    vertisol_test_1 <- filter(plot_sub, Horizon %in% grep("(?<!l)v(?!j)", plot_sub$Horizon, perl = TRUE, value = TRUE, ignore.case = TRUE) & newUpperDepth <= 100) #FLAG
    vertisol_test_2 <- filter(plot_sub, Horizon %in% grep("(?<!o)ss(?!j)", plot_sub$Horizon, perl = TRUE, value = TRUE, ignore.case = TRUE) & newUpperDepth <= 100 & Texture != "Org") #Texture is used sparingly- in case mineral entries were included in the Humus file

    vertisol <- ifelse(nrow(vertisol_test_1) >=1 & nrow(vertisol_test_2) >=1, "Vertisol", "FALSE")

    order_list[[i]] <- vertisol
      
      if(order_list[[i]] == "Vertisol")
      {next}    
       
    podzol_test1 <- filter(plot_sub, Horizon %in% grep("Bf(?!j)|Bhf(?!j)|Bh(?!j)",  plot_sub$Horizon, perl =TRUE, value = T, ignore.case = T) & newDepth >=10)
    podzol_test2 <- filter(plot_sub, Horizon %in% grep("bt(?!j)",  plot_sub$Horizon, perl =TRUE, value = T, ignore.case = T) & newUpperDepth <=50) #FLAG
    
    
    podzol <- ifelse(nrow(podzol_test1)>=1 & nrow(podzol_test2) <1, "Podzol", "FALSE")
   
    order_list[[i]] <- podzol
   
      if(order_list[[i]] =="Podzol")
      {next}

      
    gleysol_test1 <- filter(plot_sub, Horizon %in% grep("g(?!j)", plot_sub$Horizon, perl = TRUE, value = TRUE, ignore.case = TRUE) &  newUpperDepth <=50)
    
    gleysol <- ifelse(nrow(gleysol_test1)>=1, "Gleysol", "FALSE")

    order_list[[i]] <- gleysol 
    
      if(order_list[[i]] =="Gleysol")
      {next}

    solonetzic_test <- filter(plot_sub, Horizon %in% grep("Bn(?!j)",  plot_sub$Horizon, perl = TRUE, value = TRUE, ignore.case = TRUE))
    
    solonetzic <- ifelse(nrow(solonetzic_test) >= 1, "Solonetzic", "FALSE")
    
    order_list[[i]] <- solonetzic
   
      if(order_list[[i]] == "Solonetzic")
      {next}

    
    chernozem_test <- filter(plot_sub, Horizon %in% grep("Ah(?!j)(?!b)|Ahe(?!j)(?!b)|Ap(?!j)(?!b)",  plot_sub$Horizon, perl = TRUE, value = TRUE, ignore.case = TRUE) & newDepth >= 10)
    
      
    chernozem <- ifelse(nrow(chernozem_test) >= 1, "Chernozem", "FALSE")
    
    order_list[[i]] <- chernozem
   
      if(order_list[[i]] == "Chernozem")
      {next}
    
    luvisol_test <- filter(plot_sub, Horizon %in% grep("Bt(?!j)",  plot_sub$Horizon, perl = TRUE, value = TRUE, ignore.case = TRUE) & newDepth >= 5)
    luvisol <- ifelse(nrow(luvisol_test) >= 1, "Luvisol", "FALSE")
    
    order_list[[i]] <- luvisol
   
      if(order_list[[i]] == "Luvisol")
      {next}

    brunisol_test_1 <- filter(plot_sub, Horizon %in% grep("B",  plot_sub$Horizon, perl = TRUE, value = TRUE, ignore.case = FALSE) & newDepth >= 5) #this might be a problem with buried horizons, have taken out the ignore case element for now
    
    ##Indeed a problem for buried horizons: ie IC, Bmb, IIC <- Classified as Brunisol, but Should be Regosol. 
    brunisol_test_2 <- filter(plot_sub, Horizon %in% grep("b",  plot_sub$Horizon, perl = TRUE, value = TRUE, ignore.case = FALSE))
    brunisol <- ifelse(nrow(brunisol_test_1) >= 1 & nrow(brunisol_test_2) < 1, "Brunisol", "FALSE")
   
    order_list[[i]] <- brunisol
   
      if(order_list[[i]] == "Brunisol")
      {next}
  
    regosol_test <- filter(plot_sub, newDepth >= 0)
    
    regosol <- ifelse(nrow(regosol_test) >=1, "Regosol", "FALSE")
    
    order_list[[i]] <- regosol
    
    })
  }
)
27277.46 /60/60
32923.36 /60/60

output <- do.call(rbind, order_list)
output2 <- cbind(rownames(output), output)
output2 <- as.data.frame(output2) %>% dplyr::rename(PlotNumber=V1, Order = V2)
soil_order <- full_join(output2, plot.soil2)

```

```{r loop subset tests RBIND() is way too slow- needs a better alternative}

plot.soil2 <- plot.soil[1:100,]

plots <- unique(plot.soil2$PlotNumber)
loop_results <- data.frame()

system.time(
  for (i in plots){
  try({
    
    plot_sub <- plot.soil2[plot.soil2$PlotNumber==i,]
   
    cryosol_test <- filter(plot_sub, Horizon %in% grep("z(?!j)",  plot_sub$Horizon, perl =TRUE, value = T, ignore.case = T) & newUpperDepth <=100)
    
    cryosol <- plot_sub %>% mutate(Class = case_when(nrow(cryosol_test)>=1  ~ "Cryosol"))
    
    temp <- data.frame(cryosol)
    temp <- dplyr::filter(temp, Class == "Cryosol")
    
  
    loop_results <- rbind(loop_results, temp)
    cryosol <- dplyr::filter(loop_results, Class == "Cryosol" )
    
    cryosol_list <- unique(cryosol$PlotNumber)
    
    
    if(i %in% cryosol_list)
      
    {next}
    
    organic_test_1 <- filter(plot_sub, Horizon %in% grep("Of", plot_sub$Horizon, perl = TRUE, value = TRUE, ignore.case = TRUE) & newDepth >= 60)
    organic_test_2 <- filter(plot_sub, Horizon %in% grep("Om|Oh|LFH|O(?!ck)(?!ne)",plot_sub$Horizon, perl = TRUE, value = TRUE, ignore.case = TRUE) & newDepth >= 40)
    organic_test_3 <- filter(plot_sub, Cuml.Thickness >= 60)
    organic <- plot_sub %>% mutate(Class = case_when(nrow(organic_test_1) >= 1 ~ "Organic",
                                                     nrow(organic_test_2) >= 1 ~ "Organic",
                                                     nrow(organic_test_3) >= 1 ~ "Organic"))    
    
    temp <- data.frame(organic)
    temp <- dplyr::filter(temp, Class == "Organic")
    
    loop_results <- rbind(loop_results, temp)
    
    organic <- dplyr::filter(loop_results, Class == "Organic" )
    organic_list <- unique(organic$PlotNumber)
    
    if(i %in% organic_list)
    
    {next}
    
    vertisol_test_1 <- filter(plot_sub, Horizon %in% grep("v(?!j)", plot_sub$Horizon, perl = TRUE, value = TRUE, ignore.case = TRUE) & newUpperDepth <= 100)
    vertisol_test_2 <- filter(plot_sub, Horizon %in% grep("ss(?!j)", plot_sub$Horizon, perl = TRUE, value = TRUE, ignore.case = TRUE) & newUpperDepth <= 100)
    
    vertisol <- plot_sub %>% mutate(Class = case_when(nrow(vertisol_test_1) >=1 & nrow(vertisol_test_2) >=1 ~ "Vertisol"))

    temp <- data.frame(vertisol)
    temp <- dplyr::filter(temp, Class == "Vertisol")
    
    loop_results <- rbind(loop_results, temp)
    
    vertisol <- dplyr::filter(loop_results, Class == "Vertisol" )
    vertisol_list <- unique(vertisol$PlotNumber)
    
    
    if(i %in% vertisol_list)
    {next}
    
    podzol_test1 <- filter(plot_sub, Horizon %in% grep("Bf(?!j)|Bhf(?!j)|Bh(?!j)",  plot_sub$Horizon, perl =TRUE, value = T, ignore.case = T) & newDepth >=10)
    podzol_test2 <- filter(plot_sub, Horizon %in% grep("bt(?!j)",  plot_sub$Horizon, perl =TRUE, value = T, ignore.case = T) & newUpperDepth <=50)
    
    podzol <- plot_sub %>% mutate(Class = case_when(nrow(podzol_test1)>=1 & nrow(podzol_test2) <1 ~ "Podzol"))
    
    
    temp <- data.frame(podzol)
    temp <- dplyr::filter(temp, Class == "Podzol")
    
    loop_results <- rbind(loop_results, temp)
    
    podzol <- dplyr::filter(loop_results, Class == "Podzol" )
    podzol_list <- unique(podzol$PlotNumber)
    
    
    if(i %in% podzol_list)
      
    {next}
    
    gleysol_test1 <- filter(plot_sub, Horizon %in% grep("g(?!j)", plot_sub$Horizon, perl = TRUE, value = TRUE, ignore.case = TRUE) &  newUpperDepth <=50)
    
    gleysol <- plot_sub %>% mutate(Class = case_when(nrow(gleysol_test1) >= 1 ~ "Gleysol"))
    
    temp <- data.frame(gleysol)
    temp <- dplyr::filter(temp, Class == "Gleysol")
    
    loop_results <- rbind(loop_results, temp)
    gleysol <- dplyr::filter(loop_results, Class == "Gleysol" )
    gleysol_list <- unique(gleysol$PlotNumber)
    
    if(i %in% gleysol_list)
    {next}
   
    solonetzic_test <- filter(plot_sub, Horizon %in% grep("Bn(?!j)",  plot_sub$Horizon, perl = TRUE, value = TRUE, ignore.case = TRUE))
    solonetzic <- plot_sub %>% mutate(Class = case_when((nrow(solonetzic_test) >= 1 ~"Solonetzic")))
    
    temp <- data.frame(solonetzic)
    temp <- dplyr::filter(temp, Class == "Solonetzic")
    
    loop_results <- rbind(loop_results, temp)
    
    solonetzic <- dplyr::filter(loop_results, Class == "Solonetzic" )
    solonetzic_list <- unique(solonetzic$PlotNumber)
    
    if(i %in% solonetzic_list)
    {next}
    
    chernozem_test <- filter(plot_sub, Horizon %in% grep("Ah(?!j)(?!b)|Ahe(?!j)(?!b)|Ap(?!j)(?!b)",  plot_sub$Horizon, perl = TRUE, value = TRUE, ignore.case = TRUE) & newDepth >= 10)
    chernozem <- plot_sub %>% mutate(Class = case_when((nrow(chernozem_test) >= 1 ~"Chernozem")))
    
    temp <- data.frame(chernozem)
    temp <- dplyr::filter(temp, Class == "Chernozem")
    
    loop_results <- rbind(loop_results, temp)
    
    chernozem <- dplyr::filter(loop_results, Class == "Chernozem" )
    chernozem_list <- unique(chernozem$PlotNumber)
    
    if(i %in% chernozem_list)
    {next}
    
    luvisol_test <- filter(plot_sub, Horizon %in% grep("Bt(?!j)",  plot_sub$Horizon, perl = TRUE, value = TRUE, ignore.case = TRUE) & newDepth >= 5)
    luvisol <- plot_sub %>% mutate(Class = case_when((nrow(luvisol_test) >= 1 ~"Luvisol")))
    
    temp <- data.frame(luvisol)
    temp <- dplyr::filter(temp, Class == "Luvisol")
    loop_results <- rbind(loop_results, temp)
    
    luvisol <- dplyr::filter(loop_results, Class == "Luvisol" )
    luvisol_list <- unique(luvisol$PlotNumber)
    
    if(i %in% luvisol_list)
    {next}
    
    brunisol_test <- filter(plot_sub, Horizon %in% grep("B",  plot_sub$Horizon, perl = TRUE, value = TRUE, ignore.case = FALSE) & newDepth >= 5) #this might be a problem with buried horizons, have taken out the ignore case element for now
    brunisol <- plot_sub %>% mutate(Class = case_when((nrow(brunisol_test) >= 1 ~"Brunisol")))
    
    temp <- data.frame(brunisol)
    temp <- dplyr::filter(temp, Class == "Brunisol")
    
    loop_results <- rbind(loop_results, temp)
    
    brunisol <- dplyr::filter(loop_results, Class =="Brunisol")
    brunisol_list <- unique(brunisol$PlotNumber)
    
    if(i %in% brunisol_list)
    {next}
    
    regosol_test <- filter(plot_sub, newDepth >= 0)
    
    regosol <- plot_sub %>% mutate(Class = case_when(nrow(regosol_test) >=1 ~ "Regosol"))
    
    temp <- data.frame((regosol))
   
    
    loop_results <- rbind(loop_results, temp)
   
    
    
    })
  }
)
```

```{r Texture fix (older), echo =T}



Texture_to_fix <- data.frame(Texture.Unique = unique(plot.min2$Texture))
fwrite(Texture_to_fix, file = "./lookups/to_update_soil_textures.csv")


## Lookup table fix of texture codes
texture.fix <- fread("./out_data/badtexturecodestofix.csv") %>% dplyr::filter(!Texture_new == "")
plot.min2[texture.fix, Texture := i.Texture_new, on = "Texture"]
plot.min2$Texture <- plot.min2$Texture %>% toupper() %>% str_replace("SI", "Si")
min_texture.codes <- plot.min2$Texture %>% as.data.frame %>%
       drop_na() %>% filter(. != "") %>% dplyr:: rename("Texture" = 1) %>% count("Texture")
#fwrite(min_texture.codes, "./out_data/texturecodegroups.csv")

texture.codes <- codes %>% filter(ListName == "SoilTexture") %>% dplyr::rename("Texture" = Item)
min_texure.bad <- anti_join(min_texture.codes, texture.codes)
#fwrite(min_texure.bad, "./out_data/badtexturecodestofix.csv")


```

```{r Conditional tests storage, echo = TRUE}


#Cryosol

cryosol_test <- filter(plot_sub, Horizon %in% grep("z(?!j)",  plot_sub$Horizon, perl =TRUE, value = T, ignore.case = T) & Udepth <=100)


#Organic INCOMPLETE I May have to filter out all entries containing an O, and create a cumulative thickness 

organic_test_1 <- filter(plot_sub, Horizon %in% grep("Of", plot_sub$Horizon, perl = TRUE, value = TRUE, ignore.case = TRUE) & Thick <= 60)
organic_test_2 <- filter(plot_sub, Horizon %in% grep("Om|Oh|LFH|O",plot_sub$Horizon, perl = TRUE, value = TRUE, ignore.case = TRUE) & Thick <= 40)
organic_test_3 <- filter(plot_sub, Cuml.Thickness >= 60)

#Vertisolic

vertisol_test_1 <- filter(plot_sub, Horizon %in% grep("v(?!j)", plot_sub$Horizon, perl = TRUE, value = TRUE, ignore.case = TRUE) & Udepth <= 100)
vertisol_test_2 <- filter(plot_sub, Horizon %in% grep("ss(?!j)", plot_sub$Horizon, perl = TRUE, value = TRUE, ignore.case = TRUE) & Udepth <= 100)

#Podzolic

 podzol_test_1 <- filter(plot_sub, Horizon %in% grep("(Bf(?!j)|Bhf(?!j)|Bh(?!j))",  plot_sub$Horizon, perl =TRUE, value = T, ignore.case = T) & Thick >=10)
 podzol_test2 <- filter(plot_sub, Horizon %in% grep("bt(?!j)",  plot_sub$Horizon, perl = TRUE, value = TRUE, ignore.case = T) & uDepth <=50)


#Gleysolic

gleysol_test <- filter(plot_sub, Horizon %in% grep("(g(?!j))",  plot_sub$Horizon, perl = TRUE, value = TRUE, ignore.case = TRUE), & Udepth <= 50)

#Solonetzic

solonetz_test <- filter(plot_sub, Horizon %in% grep("Bn(?!j))",  plot_sub$Horizon, perl = TRUE, value = TRUE, ignore.case = TRUE))

#Chernozemic

chernozem_test <- filter(plot_sub, Horizon %in% grep("Ah(?!j)|Ahe(?!j)|Ap(?!j))",  plot_sub$Horizon, perl = TRUE, value = TRUE, ignore.case = TRUE) & Thick >= 10)

#Luvisolic

luvisol_test <- filter(plot_sub, Horizon %in% grep("Bt(?!j))",  plot_sub$Horizon, perl = TRUE, value = TRUE, ignore.case = TRUE) & Thick >= 5)

#Brunisolic

brunisol <- filter(plot_sub, Horizon %in% grep("B",  plot_sub$Horizon, perl = TRUE, value = TRUE, ignore.case = FALSE) & Thick >= 5) #this might be a problem distinguishing buried horizons..... Ignore Case was set to false to filter out 'b' horizon suffixes

#Regosolic

#Catch all?

```
=======
library(foreach)
library(doParallel)
library(dplyr)
library(data.table)
library(magrittr)
require(DBI)

```

```{r Import excel workbooks, echo = TRUE}
# setwd("C:/Users/pauld/Documents/23_BEC_Cleaning/BECMaster_Cleaning")
# plot.hum <- readxl::read_xlsx("../access_data/BECMaster64_Humus.xlsx") %>% dplyr::mutate(ID1 = "Humus", ID2 = PlotNumber, ID3 = row_number()) %>% tidyr::unite("ID_autoclass", c(ID1, ID2, ID3), sep = "_")
# plot.min <- readxl::read_xlsx("../access_data/BECMaster64_Mineral.xlsx") %>% dplyr::mutate(ID1 = "Mineral", ID2 = PlotNumber, ID3 = row_number()) %>% tidyr::unite("ID_autoclass", c(ID1, ID2, ID3), sep = "_")


hum.lookup <- read.csv("./lookups/Humus_Updated_Horizon_lookup_Table.csv")
min.lookup <- read.csv("./lookups/Mineral_Updated_Horizon_lookup_Table.csv")
```


```{r}
 becmaster <- dbConnect(odbc::odbc(), .connection_string = "Driver={Microsoft Access Driver (*.mdb, *.accdb)}; DBQ=D:/GitHub/BECMaster_Cleaning/updated_vpro/BECMaster_fixing.accdb;")
plot.env <- dbReadTable(becmaster, "BECMaster_fixing_Env") %>% mutate(Longitude = ifelse(Longitude<0, Longitude, 0-Longitude))
plot.info <- dbReadTable(becmaster, "BECMaster_fixing_Admin")
plot.min <- dbReadTable(becmaster, "BECMaster_fixing_Mineral")
plot.hum <-  dbReadTable(becmaster, "BECMaster_fixing_Humus")
dbDisconnect(becmaster)

plot.hum <- plot.hum %>% dplyr::mutate(ID1 = "Humus", ID2 = PlotNumber, ID3 = row_number()) %>% tidyr::unite("ID_autoclass", c(ID1, ID2, ID3), sep = "_")
plot.min <- plot.min %>% dplyr::mutate(ID1 = "Mineral", ID2 = PlotNumber, ID3 = row_number()) %>% tidyr::unite("ID_autoclass", c(ID1, ID2, ID3), sep = "_")
```



```{r Import ACCESS data and cleaning lookup tables}

plot.hum <- dplyr::select(plot.hum, PlotNumber, Horizon, UpperDepth, LowerDepth, Comment, ID_autoclass)

#Remove Special Characters
plot.hum$Horizon <- stringr::str_replace_all(plot.hum$Horizon, "-", "")
plot.hum$Horizon <- stringr::str_replace_all(plot.hum$Horizon, " ", "")
plot.hum$Horizon <- stringr::str_replace_all(plot.hum$Horizon, "\\(", "")
plot.hum$Horizon <- stringr::str_replace_all(plot.hum$Horizon, "\\)", "")
plot.hum$Horizon <- stringr::str_replace_all(plot.hum$Horizon, "/", "")

#Use lookup to correct Faulty Horizons -> Humus
plot.hum2 <- dplyr::left_join(hum.lookup, plot.hum) %>% dplyr::rename(Comments = Comment)

plot.hum2 <- mutate(plot.hum2, Updated_Horizon = na_if(Updated_Horizon, ""), Move_to_Mineral = na_if(Move_to_Mineral, "")) %>% 
  mutate(Move_to_Mineral = tidyr::replace_na(Move_to_Mineral, "Keep"))
plot.hum2 <- mutate(plot.hum2, Horizon.corr = dplyr::if_else(is.na(plot.hum2$Updated_Horizon), plot.hum2$Horizon, plot.hum2$Updated_Horizon)) %>% dplyr::filter(Flag_remove != "Flag")

move_to_min <- dplyr::filter(plot.hum2, Move_to_Mineral == "Move") %>% dplyr::select(-Horizon, -Updated_Horizon, -Flag_remove, -Move_to_Mineral) 
move_to_min <- dplyr::mutate(move_to_min, Texture = dplyr::if_else(Horizon.corr %in% grep("A|B|C|R", move_to_min$Horizon.corr, value = T, ignore.case = F), "Mineral_texture", "Organic"), MineralFormpH = dplyr::if_else(Horizon.corr %in% grep("A|B|C|R", move_to_min$Horizon.corr, value = T, ignore.case = F), "Mineral_no_pH", "Organic"))

plot.hum2 <- dplyr::filter(plot.hum2, Move_to_Mineral == "Keep") %>% dplyr::select(-Horizon, -Updated_Horizon, -Flag_remove, -Move_to_Mineral) 
#Use lookup to correct Faulty Horizons -> Mineral

plot.min <- dplyr::select(plot.min, PlotNumber, Horizon, UpperDepth, LowerDepth, Texture, Comments, MineralFormpH, ID_autoclass)

#Filter Special  Characters and '0'
plot.min$Horizon <- stringr::str_replace_all(plot.min$Horizon, " ", "")
plot.min$Horizon <- stringr::str_replace_all(plot.min$Horizon, "\\(", "")
plot.min$Horizon <- stringr::str_replace_all(plot.min$Horizon, "\\)", "")
plot.min$Horizon <- stringr::str_replace_all(plot.min$Horizon, "/", "")
plot.min$Horizon <- stringr::str_replace_all(plot.min$Horizon, "-", "")

plot.min <- dplyr::filter(plot.min, !Horizon %in% grep("[]0[@*!]", plot.min$Horizon, perl = TRUE, value = TRUE, ignore.case = FALSE))

#Use lookup to correct Faulty Horizons -> Mineral
plot.min2 <- dplyr::left_join(min.lookup, plot.min)

plot.min2 <- mutate(plot.min2, Updated_Horizon = na_if(Updated_Horizon, ""), Move_to_Humus = na_if(Move_to_Humus, "")) %>% 
  mutate(Move_to_Humus = tidyr::replace_na(Move_to_Humus, "Keep"))

plot.min2 <- mutate(plot.min2, Horizon.corr = dplyr::if_else(is.na(plot.min2$Updated_Horizon), plot.min2$Horizon, plot.min2$Updated_Horizon)) %>% dplyr::filter(Flag_remove != "Flag")

move_to_humus <- dplyr::filter(plot.min2, Move_to_Humus =="Move") %>% dplyr::select(-Horizon, -Updated_Horizon, -Flag_remove, -Move_to_Humus, -Texture, -MineralFormpH)

plot.min2 <- dplyr::filter(plot.min2, Move_to_Humus !="Move") %>% dplyr::select(-Horizon, -Updated_Horizon, -Flag_remove, -Move_to_Humus)
```


```{r Move Humus and Mineral Entries to the correct database- Prep data for Rbind} 
##Humus
plot.hum3 <- rbind(plot.hum2, move_to_humus) %>% mutate(MineralFormpH = "Organic", Texture = "Organic", origin = "humus") %>% 
   dplyr::mutate(Depth = UpperDepth - LowerDepth) %>%  dplyr::mutate(newUpperDepth = dplyr::if_else(Depth<0, LowerDepth, UpperDepth),
                                                     newLowerDepth = dplyr::if_else(Depth<0, UpperDepth, LowerDepth)) %>% 
  dplyr::mutate(newDepth = newUpperDepth - newLowerDepth) %>% dplyr::select(-UpperDepth, -LowerDepth, -Depth) %>% 
  mutate(Flag.Horizon.Type = "Organic.Horizon")

#Mineral

plot.min3 <- rbind(plot.min2, move_to_min) %>%  dplyr::mutate(origin = "mineral", Depth = LowerDepth - UpperDepth) %>%  dplyr::mutate(newUpperDepth = dplyr::if_else(Depth<0, LowerDepth, UpperDepth),newLowerDepth = dplyr::if_else(Depth<0, UpperDepth, LowerDepth)) %>% 
  dplyr::mutate(newDepth = newLowerDepth - newUpperDepth) %>% dplyr::select(-UpperDepth, -LowerDepth, -Depth) %>% 
  mutate(Flag.Horizon.Type = na_if(Flag.Horizon.Type, "")) %>%  mutate(Flag.Horizon.Type = tidyr::replace_na(Flag.Horizon.Type, "Mineral.Horizon")) %>% mutate(Texture = dplyr::if_else(Flag.Horizon.Type == "Organic.Horizon", "Organic", Texture))

plot.soil <- rbind(plot.min3, plot.hum3) %>% dplyr::filter(newUpperDepth >= 0, newLowerDepth >= 0, newDepth > 0) %>% #Filter nonsensical values
  dplyr::rename(Horizon = Horizon.corr) %>% dplyr::mutate(Texture = dplyr::na_if(Texture, "")) %>% dplyr::mutate(Texture = tidyr::replace_na(Texture, "no_texture")) #Fix NAs for texture. Texture will be used for organic classifaction

```

```{r Option to export cleaned databases}
#
# Compatible with join 
#

BEC_mineral <- dplyr::filter(plot.soil, ID_autoclass %in% grep("Mineral", plot.soil$ID_autoclass, value = T, perl = T)) %>% mutate(pH_info = MineralFormpH)
BEC_mineral <- left_join(BEC_mineral, plot.min, by = "PlotNumber")

BEC_humus <- dplyr::filter(plot.soil, ID_autoclass %in% grep("Humus", plot.soil$ID_autoclass, value = T, perl = T)) %>% mutate(pH_info = MineralFormpH)
BEC_humus <- left_join(BEC_humus, plot.hum, plot.min, by = "PlotNumber")


write.csv(BEC_mineral, "bec_mineral_entries.csv")
write.csv(BEC_humus, "bec_humus_entries.csv")
```

```{r Create Cumulative thickness for organic (discluding burried) and mineral horizons for organic classification}
org.cuml.thick <- dplyr::filter(plot.soil, Texture == "Organic" & !Horizon %in% grep("b", plot.soil$Horizon, value = TRUE, perl = TRUE, ignore.case = FALSE)) %>% dplyr::group_by(PlotNumber) %>% dplyr::mutate(Cuml.Thickness = sum(newDepth, na.rm = TRUE)) %>% dplyr::ungroup() %>% dplyr::mutate(Cuml.Thickness.Type = "Organic")

min.cuml.thick <- dplyr::filter(plot.soil, Texture != "Organic" | Texture == "Organic" & Horizon %in% grep("b", plot.soil$Horizon, value = TRUE, perl = TRUE, ignore.case = FALSE)) %>% dplyr::group_by(PlotNumber) %>% dplyr::mutate(Cuml.Thickness = sum(newDepth, na.rm = TRUE)) %>% dplyr::ungroup() %>% dplyr::mutate(Cuml.Thickness.Type = "Mineral")

plot.soil <- rbind(org.cuml.thick, min.cuml.thick) 
```

```{r Parallel loops for order}

plot.soil2 <- plot.soil

plot_sub <- plot.soil2  
cores=detectCores()
cl = makeCluster(cores[1]-1) 
registerDoParallel(cl)


plots <- unique(plot.soil2$PlotNumber)


system.time(
  
 x <- foreach(i = plots) %dopar% {
  
    plot_sub <- plot.soil2[plot.soil2$PlotNumber==i,]

    cryosol_test <-  dplyr::filter(plot_sub, Horizon %in% grep("(?<!H)(?<!F)(?<!y)(?<!Fa)(?<!Fm)(?<!Hh)(?<!Ha)(?<!L)(?<!Hm)(?<!H1)(?<!H2)(?<!Hd)(?<!Fq)z(?!j)",  plot_sub$Horizon, perl = TRUE, value = TRUE, ignore.case = FALSE) & newUpperDepth <=100)
    
     
    organic_test_1 <-  dplyr::filter(plot_sub, Horizon %in% grep("Of", plot_sub$Horizon, perl = TRUE, value = TRUE, ignore.case = FALSE) & newDepth >= 60)
    organic_test_2 <-  dplyr::filter(plot_sub, Horizon %in% grep("Om|Oh|LFH|O(?!f)(?!ck)(?!ne)", plot_sub$Horizon, perl = TRUE, value = TRUE, ignore.case = FALSE) & newDepth >= 40)
    organic_test_3 <- dplyr::filter(plot_sub, Cuml.Thickness >= 60 & Cuml.Thickness.Type == "Organic")
   
    organic_test_4a <- dplyr::group_by(plot_sub, Cuml.Thickness.Type, Cuml.Thickness) 
    organic_test_4a <- dplyr::summarize(organic_test_4a) 
    organic_test_4a <- dplyr::ungroup(organic_test_4a) 
    organic_test_4  <- dplyr::if_else(as.numeric(organic_test_4a[organic_test_4a$Cuml.Thickness.Type %in% "Organic", 2]) >=
                              as.numeric(organic_test_4a[organic_test_4a$Cuml.Thickness.Type %in% "Mineral", 2])*2, "Org", "Min")
    organic_test_4 <- as.data.frame(organic_test_4)
    colnames(organic_test_4) <- "Organic_test"
    organic_test_4 <- dplyr::filter(organic_test_4, Organic_test =="Org")
    
    organic_test_5 <- dplyr::filter(plot_sub, Horizon %in% grep("A(?!sh)|B|C(?!har)|R", plot_sub$Horizon, perl = TRUE, value = TRUE, ignore.case = FALSE))
    
    organic_test_6 <- dplyr::filter(plot_sub, newDepth >0)
   
    vertisol_test_1 <-  dplyr::filter(plot_sub, Horizon %in% grep("(?<!l)v(?!j)", plot_sub$Horizon, perl = TRUE, value = TRUE, ignore.case = FALSE) & !Horizon %in% grep("b",  plot_sub$Horizon, perl = TRUE, value = TRUE, ignore.case = FALSE) & newUpperDepth <= 100 & Texture != "Organic")
   
    vertisol_test_2 <-  dplyr::filter(plot_sub, Horizon %in% grep("(?<!o)ss(?!j)", plot_sub$Horizon, perl = TRUE, value = TRUE, ignore.case = FALSE) & !Horizon %in% grep("b",  plot_sub$Horizon, perl = TRUE, value = TRUE, ignore.case = FALSE) & newUpperDepth <= 100 & Texture != "Organic")
 
    podzol_test1 <- dplyr::filter(plot_sub, Horizon %in% grep("Bf(?!j)|Bhf(?!j)|Bh(?!j)",  plot_sub$Horizon, perl =TRUE, value = T, ignore.case = F) & !Horizon %in% grep("b",  plot_sub$Horizon, perl = TRUE, value = TRUE, ignore.case = FALSE) & newDepth >=10)
   
    podzol_test2 <- dplyr::filter(plot_sub, Horizon %in% grep("t(?!j)",  plot_sub$Horizon, perl =TRUE, value = T, ignore.case = F) & !Horizon %in% grep("b",  plot_sub$Horizon, perl = TRUE, value = TRUE, ignore.case = FALSE) & newUpperDepth <=50 & origin == "mineral")
    
    # gleysol_test1 <- dplyr::filter(plot_sub, Horizon %in% grep("g(?!j)", plot_sub$Horizon, perl = TRUE, value = TRUE, ignore.case = FALSE) &  newUpperDepth <=50 & newDepth >= 10 & Texture != "Organic")
    gleysol_test1 <- dplyr::filter(plot_sub, Horizon %in% grep("g", plot_sub$Horizon, perl = TRUE, value = TRUE, ignore.case = FALSE) &  newUpperDepth <=50 & newDepth >= 10 & Texture != "Organic")
        
    solonetzic_test <-  dplyr::filter(plot_sub, Horizon %in% grep("Bn(?!j)|Bnt(?!j)",  plot_sub$Horizon, perl = TRUE, value = TRUE, ignore.case = F) & !Horizon %in% grep("b",  plot_sub$Horizon, perl = TRUE, value = TRUE, ignore.case = FALSE))
     
    chernozem_test1a <- dplyr::filter(plot_sub, Horizon %in% grep("Ah(?!e)(?!j)|Ap(?!e)(?!j)",  plot_sub$Horizon, perl = TRUE, value = TRUE, ignore.case = FALSE) & !Horizon %in% grep("b",  plot_sub$Horizon, perl = TRUE, value = TRUE, ignore.case = FALSE) & Texture != "Organic")

    chernozem_test1a <- dplyr::summarize(chernozem_test1a, newUpperDepth =  min(newUpperDepth, fill = 999), newDepth = sum(newDepth))

    chernozem_test1b <- dplyr::filter(plot_sub, Horizon %in% grep("Ae(?!j)",  plot_sub$Horizon, perl = TRUE, value = TRUE, ignore.case = FALSE) & !Horizon %in% grep("b",  plot_sub$Horizon, perl = TRUE, value = TRUE, ignore.case = FALSE) & Texture != "Organic")

    chernozem_test1b <- dplyr::summarize(chernozem_test1b, newUpperDepth =  min(newUpperDepth, fill = 999), newDepth = sum(newDepth))

    chernozem_test1 <- as.data.frame(dplyr::case_when(chernozem_test1a$newUpperDepth < chernozem_test1b$newUpperDepth & chernozem_test1a$newDepth > chernozem_test1b$newDepth & chernozem_test1a$newDepth >= 10 ~ "Chernozem"))  
    
    colnames(chernozem_test1) <- "chernozem_test"
    
    chernozem_test1 <- dplyr::filter(chernozem_test1, chernozem_test =="Chernozem")

    chernozem_test2a <- dplyr::filter(plot_sub, Horizon %in% grep("Ahe(?!j)",  plot_sub$Horizon, perl = TRUE, value = TRUE, ignore.case = F)& !Horizon %in% grep("b",  plot_sub$Horizon, perl = TRUE, value = TRUE, ignore.case = FALSE) & Texture != "Organic" & newDepth >= 10)
    
    chernozem_test2b <- dplyr::filter(plot_sub, Horizon %in% grep("Ae(?!j)",  plot_sub$Horizon, perl = TRUE, value = TRUE, ignore.case = F) & !Horizon %in% grep("b",  plot_sub$Horizon, perl = TRUE, value = TRUE, ignore.case = FALSE) & Texture != "Organic"  &  newDepth >= 5)

    luvisol_test <-  dplyr::filter(plot_sub, Horizon %in% grep("Bt(?!j)",  plot_sub$Horizon, perl = TRUE, value = TRUE, ignore.case = FALSE) & !Horizon %in% grep("b",  plot_sub$Horizon, perl = TRUE, value = TRUE, ignore.case = FALSE) & Texture != "Organic" & newDepth >= 5)
   
    # brunisol_test <-  dplyr::filter(plot_sub, Horizon %in% grep("B",  plot_sub$Horizon, perl = TRUE, value = TRUE, ignore.case = FALSE) & !Horizon %in% grep("b",  plot_sub$Horizon, perl = TRUE, value = TRUE, ignore.case = FALSE) & newDepth >= 5) 
      brunisol_test <-  dplyr::filter(plot_sub, Horizon %in% grep("Bm",  plot_sub$Horizon, perl = TRUE, value = TRUE, ignore.case = FALSE) & !Horizon %in% grep("b",  plot_sub$Horizon, perl = TRUE, value = TRUE, ignore.case = FALSE) & newDepth >= 5)   
    regosol_test <- dplyr::filter(plot_sub, Horizon %in% grep("A|B|C|R",  plot_sub$Horizon, perl = TRUE, value = TRUE, ignore.case = FALSE) & newDepth > 0)
    
   
 order <-  dplyr::if_else(nrow(cryosol_test) >= 1,  "Cryosol", 
           dplyr::if_else(nrow(organic_test_1) >= 1 | nrow(organic_test_2) >= 1 | nrow(organic_test_3) >= 1|
                     nrow(organic_test_4) >=1, "Organic",
           dplyr::if_else(nrow(organic_test_5) < 1 & nrow(organic_test_6) >=1, "Organic_default",
           dplyr::if_else(nrow(vertisol_test_1) >=1 & nrow(vertisol_test_2) >=1, "Vertisol", 
           dplyr::if_else(nrow(podzol_test1)>=1 & nrow(podzol_test2) <1, "Podzol",
           dplyr::if_else(nrow(gleysol_test1)>=1, "Gleysol", 
           dplyr::if_else(nrow(solonetzic_test) >= 1, "Solonetzic", 
           dplyr::if_else(nrow(chernozem_test1)  >= 1 | nrow(chernozem_test2a) >= 1 & nrow(chernozem_test2b) < 1,
                            "Chernozem",
           dplyr::if_else(nrow(luvisol_test) >= 1, "Luvisol", 
           dplyr::if_else(nrow(brunisol_test) >= 1, "Brunisol",
           dplyr::if_else(nrow(regosol_test) >=1, "Regosol", 
                           "FALSE")))))))))))

  return(list(i, order))
 }
)

dat2 <- rbindlist(x) %>% dplyr::rename(PlotNumber = V1, Order = V2)
X1 <- full_join(dat2, plot.soil2)
fwrite(X1, "Soil_Orders.csv")
```
>>>>>>> f35e0243cd1e0532d36c077bf141d021684640fc
