---
title: "Fixing soil classificaiton and Rules based generation of soils classification "
author: "William H MacKenzie"
date: "18/12/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(reshape)
require(reshape2)
require(vegan)
require(caret)
require(tcltk)
require(randomForest)
require(Matrix)
require(labdsv)
require(gdata)
require(MASS)
require(openxlsx)
require (C50)
require(tidyr)
require(stringr)
require(rpart)
require(tree)
require(rattle)
require(rpart.plot)
require(partykit)
require(vegclust)
require(standardize)
require(dplyr)
require(tictoc)
require(plyr)
require(Hmisc)
require(data.table)
require(tidyverse)
require(psych)
require(DataExplorer)

```
# Background

This script links to a VPRO database and brings in _ENV, _MIN, _HUMUS tables for fixing 
1. fixes horizon labels formatting for both mineral and humus horizons
2. fixes obvious mixups in soil classification with lookup table
3. rules based soil classification
4. fix horizon upper/lower depth mix-ups


```{r import data}
require(DBI) #loads odbc as well
 becmaster <- dbConnect(odbc::odbc(), .connection_string = "Driver={Microsoft Access Driver (*.mdb, *.accdb)}; DBQ=D:/BECMaster64/BECMaster64.accdb;")

plot.env <- dbReadTable(becmaster, "BECMaster64_Env") %>% mutate(Longitude = ifelse(Longitude<0, Longitude, 0-Longitude))
plot.info <- dbReadTable(becmaster, "BECMaster64_Admin")
plot.humus <- dbReadTable(becmaster, "BECMaster64_Humus")
plot.min <- dbReadTable(becmaster, "BECMaster64_Mineral")
dbDisconnect(becmaster)
codes <- fread("./lookups/TableofCodes.csv", header = T, stringsAsFactors = F, strip.white = T, data.table = T)
```

### Fix horizon labels with lookup tables


```{r clean mineral horizon codes}
plot.min$Horizon_update <- plot.min$Horizon %>% stringr::str_trim()%>% stringr::str_squish() %>% str_replace_all(.," ", "")

### update obvious bad coding
min.code <- fread("./lookups/bad_mineral_horizon_codes.csv")
setDT(plot.min)[min.code, Horizon_update := Horizon_new, on = .(Horizon)]  %>% arrange(desc(PlotNumber))
##bar chart of count of codes in dataset

min_horizons <- plot.min$Horizon_update %>% as.data.frame %>%
       drop_na() %>% filter(. != "") %>% dplyr:: rename("Horizon" = 1) %>%
   group_by(Horizon) %>% tally() %>% filter(n>=25 & n<35) 
ggplot(min_horizons, aes(x = reorder(Horizon, -n), y = n)) + geom_bar(stat = "identity")

fwrite(plot.min, "./clean_data/Mineral_HorizonCode_updated.csv", row.names = FALSE, col.names = TRUE)
```

```{r fix mineral horizon depth orders and data coding issues}
#Add total depths
plot.min2 <- plot.min %>% dplyr::select(PlotNumber, Horizon, UpperDepth, LowerDepth, Texture, PercentCoarseFragsTotal) %>% 
  mutate(Depth = LowerDepth - UpperDepth)

plot.min2 <- plot.min2 %>% mutate(newUpperDepth = ifelse(Depth<0, LowerDepth, UpperDepth)) %>% 
    mutate(newLowerDepth = ifelse(Depth<0, UpperDepth,LowerDepth)) %>% 
  mutate(newDepth = newLowerDepth - newUpperDepth) %>% dplyr::select(-UpperDepth, -LowerDepth, -Depth)

plot.min2$Texture <- plot.min2$Texture %>% toupper() %>% str_replace("SI", "Si") %>% str_trim()

## Lookup table fix of texture codes
texture.fix <- fread("./out_data/badtexturecodestofix.csv") %>% dplyr::filter(!Texture_new == "")
plot.min2[texture.fix, Texture := i.Texture_new, on = "Texture"]
plot.min2$Texture <- plot.min2$Texture %>% toupper() %>% str_replace("SI", "Si")
min_texture.codes <- plot.min2$Texture %>% as.data.frame %>%
       drop_na() %>% filter(. != "") %>% dplyr:: rename("Texture" = 1) %>% count("Texture")
#fwrite(min_texture.codes, "./out_data/texturecodegroups.csv")

texture.codes <- codes %>% filter(ListName == "SoilTexture") %>% dplyr::rename("Texture" = Item)
min_texure.bad <- anti_join(min_texture.codes, texture.codes)
#fwrite(min_texure.bad, "./out_data/badtexturecodestofix.csv")
```
# #### Soil classification
# Many bad codes, truncated codes, reversal of subgroup and group codes, and wrong classifications (based on horizon info). Automatic updates in many cases are probably not universally correct.  Need Rules based classification in part

```{r old code for soil classification repair}
# plot.env$SoilClassGroup <-  plot.env$SoilClassGroup %>% stringr::str_trim() %>% stringr::str_squish()
# plot.soilclass <- plot.env %>% dplyr::select(PlotNumber, SoilClassGroup, SoilClassSubGroup) %>% data.frame
# soil.classes <- codes %>% filter(ListName == "SoilClassGroup") %>% dplyr::rename("SoilClassGroup" = Item)
# soil.subgroups <- codes %>% filter(ListName == "SoilClassSubGroup") %>% dplyr::rename("SoilClassSubGroup" = Item)
#
# ##update based on lookup table
# soil.fix <- fread("./out_data/bad_soilGroups_update2.csv", data.table = T, strip.white = F)%>% filter(!Group_updated == "")
# #soil.fix[soil.fix == ""] <- NA
# setDT(plot.soilclass)[soil.fix, c("SoilClassGroup", "SoilClassSubGroup") := list(Group_updated, SubGroup_updated), on = .(SoilClassGroup, SoilClassSubGroup)]
# plot.soilclass1 <- plot.soilclass %>% filter(!is.na(SoilClassGroup)) %>% arrange(desc(PlotNumber))
# fwrite(plot.soilclass1, "./clean_data/soilclass_updates.csv")
# plot.soilclass.sum <- plot.soilclass1 %>% dplyr::select(-PlotNumber) %>%  group_by(SoilClassGroup, SoilClassSubGroup) %>% tally()
# fwrite(plot.soilclass.sum, "./out_data/all_soilclass.csv")
# bad.soil.class2 <- anti_join(plot.soilclass, soil.classes, by="SoilClassGroup") %>% dplyr::select(-PlotNumber) %>%  group_by(SoilClassGroup, SoilClassSubGroup) %>% tally()
# fwrite(bad.soil.class2, "./out_data/bad_soilGroups.csv")


# ## create other fixes
# ##remove spaces
# plot.soilclass$Group_updated <-   stringr::str_trim(plot.soilclass$SoilClassGroup, side = "both") %>% stringr::str_squish()
# plot.soilclass$SubGroup_updated <-   stringr::str_trim(plot.soilclass$SoilClassSubGroup, side = "both") %>% stringr::str_squish()
# plot.soilclass <- plot.soilclass %>%   mutate_all(list(~na_if(., ""))) %>%  mutate_all(list(~na_if(.," "))) %>%  mutate_all(list(~na_if(.,"  "))) %>%  mutate_all(list(~na_if(.,"   ")))%>%  mutate_all(list(~na_if(.,"    ")))%>%  mutate_all(list(~na_if(.,"     "))) %>% filter(!is.na(SoilClassGroup) | !is.na(SoilClassSubGroup) )
# plot.soilclass <- plot.soilclass %>% data.frame %>% mutate(Group_updated = toupper(Group_updated), SubGroup_updated = toupper(SubGroup_updated))
#
# ## remove leading periods
# plot.soilclass2 <- plot.soilclass %>% filter(grepl("^[.]", SoilClassGroup))
# plot.soilclass2$SoilClassGroup_new <- str_replace_all(plot.soilclass2$SoilClassGroup,"[.]", "")
# setDT(plot.soilclass)[plot.soilclass2, Group_updated  := SoilClassGroup_new, on = "PlotNumber"]
# #plot.soilclass <- plot.soilclass %>% data.frame %>% mutate(Group_updated  = ifelse(Group_updated  == "NA", "X", Group_updated ))
#
# ## split codes with periods
# plot.soilclass2 <- as.data.frame(plot.soilclass) %>% filter(grepl("[.]", SoilClassGroup))
# plot.soilclass2[c('SoilClassGroup_new', 'SoilClassSubGroup_new')] <- str_split_fixed(plot.soilclass2$SoilClassGroup, '[.]', 2)
# setDT(plot.soilclass)[plot.soilclass2, Group_updated  := SoilClassGroup_new, on = "PlotNumber"]
# setDT(plot.soilclass)[plot.soilclass2, SubGroup_updated := SoilClassSubGroup_new, on = "PlotNumber"]
#
# ## split codes with space
# plot.soilclass2 <- as.data.frame(plot.soilclass) %>% filter(grepl(" ", SoilClassGroup))
# plot.soilclass2[c('SoilClassGroup_new', 'SoilClassSubGroup_new')] <- str_split_fixed(plot.soilclass2$SoilClassGroup, ' ', 2)
# setDT(plot.soilclass)[plot.soilclass2, Group_updated := SoilClassGroup_new, on = "PlotNumber"]
# setDT(plot.soilclass)[plot.soilclass2, SubGroup_updated := SoilClassSubGroup_new, on = "PlotNumber"]

#fwrite(plot.soilclass, "./clean_data/soilclass_updates.csv")

# bad.soil.class2 <- anti_join(plot.soilclass, soil.classes, by=c('Group_updated'='SoilClassGroup')) %>% select(-PlotNumber) %>%  group_by(SoilClassGroup, SoilClassSubGroup) %>%
#   tally() %>% filter(n>100)
# ggplot(bad.soil.class2, aes(x = reorder(SoilClassGroup, -n), y = n)) + geom_bar(stat = "identity")
# fwrite(bad.soil.class2, "./out_data/bad_soilGroups.csv")

#
# ## fix case and update from lookup table
# plot.soilclass.tst <- plot.soilclass2
# plot.soilclass.tst[is.na(plot.soilclass.tst)] <- "xxx"
# setDT(plot.soilclass.tst)[soil.fix, c("SoilClassGroup", "SoilClassSubGroup") := list(Group_new, Subgroup_new), on = .(SoilClassGroup, SoilClassSubGroup)]
# bad.soil.class.tst <- anti_join(plot.soilclass.tst, soil.classes, by = "SoilClassGroup") %>% select(-PlotNumber) %>%  group_by(SoilClassGroup, SoilClassSubGroup) %>% tally()
#
# ###bar chart of count of codes in dataset
# ggplot(bad.soil.form, aes(x = reorder(soilForm, -n), y = n)) + geom_bar(stat = "identity")
#
#
# #bad.soil$soilForm <- bad.soil$soilForm
# bad.soil.codes <- bad.soil %>% select(soilForm) %>% unique
# #fwrite(bad.soil.codes, "./out_data/badcodestofix.csv")

```





Soil Texture Classes
4 classes for association report
Fine - See def in LMH 25
Medium Fine - Non-skeletal soils that are not fine (<35% c.f.)
Medium Coarse - Skeletal soils that are not coarse (35-70% c.f.)
Coarse - see def in LMH25

```{r TEXTURE group codes for SIVI}
text.groups <- fread("./out_data/texturecodegroups.csv")

plot.min2[text.groups, text.group := i.Text_group, on = "Texture"]
plot.min2$text.groups.cf <- "M" 
plot.min2 <- plot.min2 %>% mutate(text.groups.cf = ifelse((text.group %in% c("C") & PercentCoarseFragsTotal >=35), "C", text.groups.cf))

plot.min2 <- plot.min2 %>%  mutate(text.groups.cf = ifelse((text.group %in% c("MC", "M") & PercentCoarseFragsTotal >=70), "C", text.groups.cf))# %>% filter(text.group == "M")

plot.min2 <- plot.min2 %>% mutate(text.groups.cf = ifelse((text.group %in% c("F", "MF")& (is.na(PercentCoarseFragsTotal) | PercentCoarseFragsTotal <20)), "F", text.groups.cf)) #%>% filter(text.group == "F")

plot.min2 <- plot.min2 %>% mutate(text.groups.cf = ifelse(is.na(text.group), NA, text.groups.cf)) #%>% filter(text.group == "F")
#plot.min2 <- plot.min2 %>% mutate(text.groups.cf = ifelse((!is.na(text.group) & is.na(text.groups.cf)) ,"M", text.groups.cf)) #%>% filter(text.group == "F")

#plot.min2 <- plot.min2 %>% mutate(text.groups.cf = ifelse((text.group %in% c("MC", "M") & (PercentCoarseFragsTotal >35 & PercentCoarseFragsTotal<70)), "MC","M"))# %>% filter(text.group == "F")

xx <- plot.min2 %>% filter(str_detect(Horizon, "O"))
```



#### Update the plot quality fields for soils

```{r Update Admin }

```


